Spontaneous Similarity Judgments of Musical Tones played with various Playing Techniques

### 2017-12-18 paper/lagrangeSpontaneousSimilarity2017.tex
metric subsec

The performance of the different methods are evaluated in a ranking setting. The well known precision at rank $k$ is thus considered, with $k=5$.

>>>>

The performance of the different methods are evaluated in a ranking setting. The precision at rank $k$ is thus considered, with $k=5$. For one sound recording termed the query, the $k$ the nearest other sound recordings are retrieved. The precision is then the ratio of those sound recordings that have the same label as the query in the grouping we consider as reference. This process is repeated for each sound recordings taken as query, and the performance is averaged over the queries.
